\section{Goals}

The work described here represents initial steps in our efforts to:

\begin{itemize}[label=\raisebox{0.25ex}{\tiny$\bullet$}]

\item Understand and describe the native data model and operation history of OpenRefine using the concepts and terminologies of the reproducible research and provenance communities.

\item Discover what provenance queries can be supported by the OpenRefine data model and operation history.  Demonstrate queries that reveal key aspects of the provenance of cleaned data sets.

\item Extend the YesWorkflow \cite{mcphillips2015yesworkflowa, yw-website} process, data, and provenance models as needed to represent the operations, transformations, data structures, data flows, and data dependencies that characterize data cleaning workflows.  

%\item Employ YesWorkflow to represent end-to-end workflows carried out using OpenRefine so that they can be visualized readily and queried prospectively.

\item Identify provenance queries important for achieving research transparency that apparently \emph{cannot} be satisfied using just the information recorded by OpenRefine. Develop means to augment the operation history with additional information needed to support these critical queries.

\item Employ computational environments that can be reproduced reliably across multiple computer systems maintained by different research team members. 

\item Enable members of the community to independently repeat our experiments and demonstrations, and to reproduce, review, and evaluate our results on their own computers.

\end{itemize}
